THESIS PROJECT PROPOSAL

### 2019-11-07 project_ashish/paper.tex
commit

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/pg.png}
  \caption{Important production processes of Standard model the Higgs boson in proton collisions.}
   \label{figure 2}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/tq.png}
  \caption{Important production processes of the Higgs boson in proton collisions.}
   \label{figure 3}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd7.png}
  \caption{ATLAS-CMS combined measurements of coupling strength modifiers.}
   \label{figure 4}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/lum6.png}
  \caption{\onehalfspacing Projected performance of the LHC until 2038, which shows the dates
Preliminary for prolonged stops (LS) of the LHC and luminosities. Points
show instant brightness while the line shows brightness accumulated.}
   \label{figure 5}
\end{figure}

@@

\section{PROPOSAL}
- what we will do:  search for tH events, using which channels.

@@

\section{GENERAL OBJECTIVE}
- motivation, tH production crossection, sign of $k_t$, search for BSM, ..

>>>>

\begin{figure}
  \centering
   \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/pg.png}
  \caption{Important production processes of Standard model the Higgs boson in proton collisions.}
   \label{figure 2}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/tq.png}
  \caption{Important production processes of the Higgs boson in proton collisions.}
   \label{figure 3}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[scale=0.5]{/home/ashish/Desktop/cd7.png}
  \caption{ATLAS-CMS combined measurements of coupling strength modifiers.}
   \label{figure 4}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/lum6.png}
  \caption{\onehalfspacing Projected performance of the LHC until 2038, which shows the dates
Preliminary for prolonged stops (LS) of the LHC and luminosities. Points
show instant brightness while the line shows brightness accumulated.}
   \label{figure 5}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms.png}
  \caption{\onehalfspacing Leading order Feynman diagrams for the associated production of a single top quark and a Higgs boson in the t channel, where the Higgs boson couples either to the top quark (left) or the W boson (right).}
   \label{figure 6}
\end{figure}

@@

\section{PROPOSAL}

- what we will do:  search for tH events, using which channels.

@@

\section{GENERAL OBJECTIVE}

- motivation, tH production crossection, sign of $k_t$, search for BSM, ..
